Implementing simplified INLA into `aghq`

### 2022-11-21 src/dev_sinla/sinla.Rmd
Attempting to get new AGHQ Laplace to work

```{r}
ks_gaussian_tmbstan <- lapply(1:length(mode), function(i) {
  samples_gaussian_i <- filter(samples_gaussian, index == i)$value
  samples_tmbstan_i <- filter(samples_tmbstan, index == i)$value
  inf.utils::ks_test(samples_gaussian_i, samples_tmbstan_i)
})

ks_laplace_tmbstan <- lapply(1:length(mode), function(i) {
  samples_laplace_i <- filter(samples_laplace, index == i)$value
  samples_tmbstan_i <- filter(samples_tmbstan, index == i)$value
  inf.utils::ks_test(samples_laplace_i, samples_tmbstan_i)
})

@@

@@

for(z in 1:length(modesandhessians$weights)) {
  theta <- as.numeric(modesandhessians[z, thetanames])
  mode_i <- as.numeric(modesandhessians$mode[[z]][i])
  Sigma <- solve(modesandhessians$H[[z]])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  pdf <- pdf + exp(dnorm(x_test_value, mean = mode_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z]))
}

@@

## Full Laplace approximation

@@

@@

for(theta in thetanames) param_i_fixed_theta[[theta]] <- modesandhessians[z, thetanames][[theta]]

@@

for(z in 1:length(modesandhessians$weights)) {
  theta <- as.numeric(modesandhessians[z, thetanames])

@@

>>>>

```{r}
ks_gaussian_tmbstan <- lapply(1:length(x_hat), function(i) {
  samples_gaussian_i <- filter(samples_gaussian, index == i)$value
  samples_tmbstan_i <- filter(samples_tmbstan, index == i)$value
  inf.utils::ks_test(samples_gaussian_i, samples_tmbstan_i)
})

ks_laplace_tmbstan <- lapply(1:length(x_hat), function(i) {
  samples_laplace_i <- filter(samples_laplace, index == i)$value
  samples_tmbstan_i <- filter(samples_tmbstan, index == i)$value
  inf.utils::ks_test(samples_laplace_i, samples_tmbstan_i)
})

@@

```{r}
ks_results %>%
  group_by(type) %>%
  summarise(D = mean(D))
```

@@

for(z in 1:nrow(modesandhessians)) {
  theta <- as.numeric(modesandhessians[z, thetanames])
  mode_i <- as.numeric(modesandhessians$mode[[z]][i])
  Sigma <- solve(modesandhessians$H[[z]])
  sd_i <- as.numeric(sqrt(Sigma[i, i]))
  pdf <- pdf + exp(dnorm(x_test_value, mean = mode_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z]))
}

@@

## Full Laplace approximation (old way)

@@

```{r}
#' All of the theta
modesandhessians[, thetanames]

#' Just the zth one
theta <- as.numeric(modesandhessians[z, thetanames])
theta

- h_norm(theta)
```

@@

for(theta_string in thetanames) param_i_fixed_theta[[theta_string]] <- modesandhessians[z, thetanames][[theta_string]]

@@

for(z in 1:nrow(modesandhessians)) {
  theta <- as.numeric(modesandhessians[z, thetanames])

@@

## Full Laplace approximation (new way)

The method above for doing quadrature over the full Laplace approximation should work, but it requires a lot of computation.
Instead, we might be able to do this more cost effectively by integrating $\theta$ out before normalising $\tilde p_\text{LA}(x_i, \theta(z), y)$.
This would look like first obtaining
$$
\tilde p(x_i, y) = \sum_z \tilde p_\text{LA}(x_i, \theta(z), y) \omega(z),
$$
then normalising by the previously obtained $\tilde p_\text{AQ}(y)$ as follows
$$
\tilde p(x_i \, | \, y) = \frac{\tilde p(x_i, y)}{\tilde p_\text{AQ}(y)}.
$$

```{r}
#' Always (?) want the same initialisation parameters (though they probably could be better right?)
param_i_fixed_theta <- list(
  beta_prev = 0, 
  phi_prev_i = 0, 
  phi_prev_minus_i = rep(0, data$n - 1),
  log_sigma_phi_prev = 0
)

#' Always fixing the hyperparameters
map_fixed_theta <- list(beta_prev = factor(NA), log_sigma_phi_prev = factor(NA))

#' Going to store the functions p_LA(x_i, theta(z), y) in objs
objs <- list()

for(z in 1:nrow(modesandhessians)) {
 theta <- as.numeric(modesandhessians[z, thetanames])

  for(theta_string in thetanames) param_i_fixed_theta[[theta_string]] <- modesandhessians[z, thetanames][[theta_string]]

  objs[[z]] <- obj_fixed_theta
}

aghq_laplace_marginal <- function(x) {
  pdf <- 0
  for(z in 1:nrow(modesandhessians)) {
    pdf <- pdf + exp(as.numeric(-objs[[z]]$fn(x))) * modesandhessians[z, "weights"]
  }
  return(pdf)
}

#' Issue is that we do the normalisation after now..
aghq_laplace_marginal(x = x_test_value)
aghq_laplace_marginal(x = -1)
```
